Publicity Outreach for ``Quantum interval-valued probability: Contextuality and the Born rule''

### 2018-04-24 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updated by me...

\maketitle
Since randomness is exploited in cryptography, algorithmic complexity,
and gambling, people are always seeking reliable random sources. Quantum
physics could provide a reliable random source since it is widely
believed that the results of quantum measurements have no way to be
predicted deterministically. More precisely, this fact, called the
Kochen-Specker theorem, states that quantum physics cannot be simulated
by a classical non-contextual hidden-variable model. However, its
main tenet has been questioned because finite-precision measurements,
i.e., errors in preparation or observation, might invalidate its spirit.
Our work, by introducing an interval-valued probabilistic framework,
establishes bounds on the validity of the Kochen-Specker theorem in
realistic, i.e., error-non-free, experimental environments. The conclusion
is that a quantum theory of measurement that includes errors in the
probability outcomes can still be contextuality, as long as the error
is bounded by a finite amount. This also provides additional trust
of the randomness of quantum random sources.

>>>>

\maketitle
Since randomness is exploited in cryptography, algorithmic complexity,
and gambling, people are always seeking reliable random sources. Quantum
physics could provide a reliable random source since it is widely
believed that the results of quantum measurements cannot be predicted
deterministically. More precisely, this fact, called the Kochen-Specker
theorem, states that quantum physics cannot be simulated by a classical
non-contextual hidden-variable model. However, its main tenet has
been questioned because its spirit might be invalidated by finite-precision
measurements, i.e., errors in preparation or observation. Our work,
by introducing an interval-valued probabilistic framework, establishes
bounds on the validity of the Kochen-Specker theorem in realistic,
i.e., error-non-free, experimental environments. We found that a quantum
theory of measurement that includes errors in the probability outcomes
can still be contextual, as long as the error is bounded by a finite
amount. This conclusion also provides additional trust of the randomness
of quantum random sources.
